Resilience plots

### 2017-12-27 analysis/resilience-plots.Rmd
add resilience plots

---
title: "Anovas RWI Resilience"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Dec"
output:
  md_document:
    variant: markdown_github
bibliography: ../references.bib 
csl: ../ecology.csl
---

@@

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("dplR")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('stringr')
library('pander')
library('broom')
library('effects')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
library('car')
library('auxiliar')
library('WRS2')
library('MASS')
library('rcompanion')
```

>>>>

---
title: "Resilience plots"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Dec"
output:
  md_document:
    variant: markdown_github
bibliography: ../references.bib 
csl: ../ecology.csl
---

@@

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("dplR")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('stringr')
library('pander')
library('broom')
library('effects')
```

# Cargar los datos
```{r}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep = '')
```

```{r}
re_bai <- read.csv(file=paste0(di, 'data/resilience/resilience_bai.csv'), header=TRUE, sep=',')
re_evi <- read.csv(file=paste0(di, 'data/resilience/resilience_evi.csv'), header=TRUE, sep=',')
```

bai <- re_bai %>% dplyr::select(-tree, -rrs) %>% mutate(mivariable = "BAI")
evi <- re_evi %>% dplyr::select(-iv_malla_modi_id, -rrs) %>% mutate(mivariable = "EVI")
